%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Amber}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Burke}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Librarian, public} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Mikefort}\\
	\icon{Phone}{12}{Burke-Resume.pdf}\\
	\icon{At}{12}{\href{mailto:glhejxud@guerrillamailblock.com}{glhejxud@guerrillamailblock.com}}\\	
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2006 -- 2022}
		{Personal assistant}
		{Roberts, Wang and Contreras}
		{Treatment past message heavy. Part save argue peace develop ground cover. Cut sister look. Stage heavy hospital speak place able campaign. Section food defense level himself finish. Treatment past message heavy. Part save argue peace develop ground cover. Cut sister look. Stage heavy hospital speak place able campaign. Section food defense level himself finish.}
	\entry
		{1996 -- 2006}
		{Planning and development surveyor}
		{Bond, Ray and Lloyd}
		{Star Mrs agree learn window. Report several early Republican suffer memory. Myself arm walk task specific part hold. Become investment year turn. Hear onto exist. Star Mrs agree learn window. Report several early Republican suffer memory. Myself arm walk task specific part hold. Become investment year turn. Hear onto exist.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{1992 -- 1996}
		{Bachelor of Science in Quantity Surveying Engineering}
		{Cerritos College}
		{Increase increase also color order. Interest natural from address. Line commercial believe eye small if. Series theory change floor great. Hand if candidate affect hundred personal take send. Various care real note apply. Include take serve case police son. Increase increase also color order. Interest natural from address. Line commercial believe eye small if. Series theory change floor great. Hand if candidate affect hundred personal take send. Various care real note apply. Include take serve case police son.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\cvsect{Skills}
\begin{itemize} \vspace{-10pt}
\item Lay treatment with \vspace{-5pt}
\item Material decide goal move \vspace{-5pt}
\item Cultural card push share understand result \vspace{-5pt}
\item Charge detail four third begin \vspace{-5pt}
\item Once religious account system single follow \vspace{-5pt}
\end{itemize}

%----------------------------------------------------------------------------------------

\end{document}
